Andres Karjus

### 2019-06-09 news.Rmd
news links now open in new tab

---
title: ''
output: html_document
theme: spacelab
---

<style>
.main-container {
  padding: 0px;
}
ul{
  padding-left: 16px;
}
</style>

>>>>

---
title: ''
output: html_document
theme: spacelab
---
<head>
<base target="_blank">
</head>
<style>
.main-container {
  padding: 0px;
}
ul{
  padding-left: 16px;
}
</style>
